---
title: "OIA computation"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

# Libraries

```{r load_libraries_specific, include = FALSE}
library(patchwork)
library(ggalluvial)
library(marelac)
library(ggdist)
library(kableExtra)
library(khroma)
library(ggh4x)
library(ggpattern)
library(colorspace)
library(stars)
library(seacarb)
```

```{r select_basinmask_5}

basinmask <- basinmask %>% 
  filter(MLR_basins == "5") %>% 
  select(lon, lat, basin)

```


```{r define_paths_to_access_eMLR_files, include = FALSE}

# only path_observations needs to be changed to model
path_observations <-
  paste0(path_root, "/observations/")

path_preprocessing    <-
  paste0(path_observations, "preprocessing/")


path_preprocessing_model    <-
  paste0(path_root, "/model/preprocessing/")

path_out <-   paste0(path_observations, "output_publication/")
path_OIA <-   "/nfs/kryo/work/jenmueller/ocean_interior_acidification/"


```

# Read data

## Delta Cant

```{r read_interior_dcant_files}

file_out <- paste0(path_out, "dcant_emlr_cstar_mueller_94-04-14.nc")

dcant_3d_read_mdim <-
  read_mdim(file_out)

ggplot() +
  geom_stars(data = dcant_3d_read_mdim %>% 
               filter(period == "1994 - 2004",
                      depth == 50)) +
  facet_grid(MLR_basins~Version_ID_group) +
  scale_fill_viridis_b(breaks = c(-Inf, seq(0,16,2), Inf),
                       na.value = "transparent")


dcant_3d_tibble <- dcant_3d_read_mdim %>% 
               # filter(Version_ID_group == "Standard case",
               #        MLR_basins == "3") %>% 
  as_tibble()

rm(dcant_3d_read_mdim)

dcant_3d_tibble <- dcant_3d_tibble %>% 
  drop_na()


dcant_3d_tibble <- dcant_3d_tibble %>%
  mutate(dcant = if_else(dcant < 0, 0, dcant))

# dcant_3d_tibble <- dcant_3d_tibble %>%
#   filter(lon == 335.5,
#          lat == 0.5)


dcant_3d_tibble %>%
  filter(depth == 500,
         Version_ID_group == "Standard case",
         MLR_basins == "3") %>%
  ggplot() +
  geom_raster(aes(lon, lat, fill = dcant)) +
  facet_grid(MLR_basins ~ Version_ID_group) +
  scale_fill_viridis_b(breaks = c(-Inf, seq(0, 16, 2), Inf),
                       na.value = "transparent")

# dcant_3d_tibble %>% 
#   ggplot() +
#   geom_path(aes(dcant, depth, col = period)) +
#   scale_y_reverse()

```

```{r tcant_sabine_2004}

S04_cant_3d <-
  read_csv(paste(path_preprocessing,
                 "S04_tcant_3d.csv",
                 sep = "")) %>% 
  mutate(tcant = if_else(tcant < 0, 0, tcant))

```


# Required data

## Observational

Currently, following data sets are used for mapping:

- GLODAPv2_2016b_MappedClimatologies, with variables  
  - Phosphate (-> phosphate_star)
  - Silicate
  - Oxygen (-> AOU)
  - TAlk (surface only)
  - TCO2 (surface only)


```{r load_GLODAPv2_2016b_MappedClimatologies_interior_mapping}

variables <-
  c("TCO2", "TAlk", "PO4", "silicate", "NO3")

# i_variable <- variables[1]

for (i_variable in variables) {
  temp <- read_csv(paste(
    path_preprocessing,
    paste("GLODAPv2_2016_MappedClimatology_", i_variable, ".csv", sep = ""),
    sep = ""
  ))
  
  if (exists("GLODAP_predictors")) {
    GLODAP_predictors <- full_join(GLODAP_predictors, temp)
  }
  
  if (!exists("GLODAP_predictors")) {
    GLODAP_predictors <- temp
  }
}

rm(temp, i_variable, variables)

GLODAP_predictors <- GLODAP_predictors %>%
  rename(phosphate = PO4,
         nitrate = NO3,
         talk = TAlk,
         tco2 = TCO2)

# removed na's attributable to slightly different coverage of predictor fields
GLODAP_predictors <- GLODAP_predictors %>%
  drop_na()

```



- World Ocean Atlas 2018  
  - Salinity
  - Temperature
  - Neutral density

```{r load_WOA18}

WOA18_predictors <-
  read_csv(paste(path_preprocessing,
                 "WOA18_sal_temp.csv",
                 sep = ""))

WOA18_predictors_nuts_O2 <-
  read_csv(paste(path_preprocessing,
                 "WOA18_nuts_O2.csv",
                 sep = ""))

```

# Join data

## WOA18 + GLODAP

WOA18 and GLODAP predictor climatologies are merged. Only horizontal grid cells with observations from both predictor fields are kept.

```{r join_WOA18_GLODAP_predictors}

# join deep water predictors

predictors <- right_join(GLODAP_predictors,
                          WOA18_predictors)

predictors <- rquery::natural_join(predictors, WOA18_predictors_nuts_O2,
                           by = c("lon", "lat", "depth", "basin_AIP"),
                           jointype = "LEFT") %>% 
  as_tibble()

predictors <- predictors %>% 
  drop_na()


rm(GLODAP_predictors, WOA18_predictors_nuts_O2, WOA18_predictors)

```

## predictors + Cant

```{r join_predictors_dcant}

# predictors %>% distinct(depth) %>% pull()
# S04_cant_3d %>% distinct(depth) %>% pull()
# dcant_3d_tibble %>% distinct(depth) %>% pull()

DIC_1994 <- 
  inner_join(predictors,
             dcant_3d_tibble %>% filter(period == "1994 - 2004") %>% 
               select(-period))


DIC_1994 <- DIC_1994 %>% 
  mutate(tco2 = tco2 - 0.8 * dcant)

DIC_2004 <- DIC_1994 %>% 
  mutate(tco2 = tco2 + dcant)

DIC_2014 <-
  inner_join(DIC_2004 %>% select(-dcant),
             dcant_3d_tibble %>% filter(period == "2004 - 2014") %>%
               select(-period))

DIC_2014 <- DIC_2014 %>% 
  mutate(tco2 = tco2 + dcant)


DIC_1800 <- inner_join(
  DIC_1994 %>%   filter(Version_ID_group == "Standard case",
                        MLR_basins == "3"),
  S04_cant_3d %>% select(lon, lat, depth, tcant)
)

DIC_1800 <- DIC_1800 %>% 
  mutate(tco2 = tco2 - tcant)

DIC <- bind_rows(
  DIC_1800 %>% mutate(tref = "1800"),
  DIC_1994 %>% mutate(tref = "1994"),
  DIC_2004 %>% mutate(tref = "2004"),
  DIC_2014 %>% mutate(tref = "2014")
)

rm(DIC_1800, DIC_1994, DIC_2004, DIC_2014, predictors, dcant_3d_tibble, S04_cant_3d)

cases <- DIC %>%
  distinct(tref, Version_ID_group, MLR_basins)


```

# Compute acidification trends

```{r compute_acidification_trends}

acidification <- DIC %>%
  mutate(
    carb(
      flag = 15,
      var1 = talk * 1e-6,
      var2 = tco2 * 1e-6,
      S = sal,
      T = temp,
      P = depth / 10,
      Pt = phosphate * 1e-6,
      Sit = silicate * 1e-6,
      k1k2 = "s20",
      kf = "dg"
    )
  )

rm(DIC)

acidification <- acidification %>%
  select(-c(dcant, tcant, flag, S, T, Patm, P, DIC, ALK))

acidification <- acidification %>%
  mutate(hyd_ion = 10^(-pH))


calc_delta_total <- function(x) (x - first(x))
calc_delta_interval <- function(x) (x - lag(x, default = first(x)))

acidification_trend <- acidification %>% 
  arrange(tref) %>% 
  group_by(lat, lon, depth, Version_ID_group, MLR_basins) %>% 
  mutate(
    across(
      .cols = c(tco2, pH, pCO2insitu, HCO3, CO3, OmegaAragonite, OmegaCalcite, hyd_ion),
      .fns = list(delta_total = calc_delta_total, delta_interval = calc_delta_interval)
    )
  ) %>% 
  ungroup()

rm(acidification)


```


# Write ouput

```{r write_output_files}

acidification_trend %>% 
  write_csv(paste0(path_OIA, "OIA_all.csv"))

# read_csv(paste0(path_OIA, "OIA_all.csv"))


acidification_trend %>%
  filter(Version_ID_group == "Standard case",
         MLR_basins == "3") %>%
  write_csv(paste0(path_OIA, "OIA_standard_case.csv"))



```


```{r write_output_files_stars, eval=FALSE}



# convert from tibble to stars object
acidification_trend_stars <- st_as_stars(
  acidification_trend,
  dims = c(
    "lon",
    "lat",
    "depth",
    "tref",
    "MLR_basins",
    "Version_ID_group"
  )
)

# assign coordinate system to horizontal (lon, lat) coordinates
# st_crs(dcant_inv_out_stars) <- "+proj=longlat"
st_crs(acidification_trend_stars) <- st_crs(4326)

# plot variable per depth level
# ggplot() +
#   geom_stars(data = acidification_trend_stars %>% 
#                filter(period == "1994 - 2004",
#                       depth == 50)) +
#   facet_grid(MLR_basins~Version_ID_group) +
#   scale_fill_viridis_b(breaks = c(-Inf, seq(0,16,2), Inf),
#                        na.value = "transparent")


file_out <- paste0(path_OIA, "OIA_pH.nc")

# write stars object to .nc file

names_OIA <-
  acidification_trend_stars %>%
  names()

acidification_trend_stars %>% 
  select(names_OIA[12]) %>% 
  write_mdim(file_out)

# # reopen .nc file with all available stars functions
# dcant_3d_read_ncdf <-
#   read_ncdf(file_out)
# dcant_3d_read_mdim <-
#   read_mdim(file_out)
# 
# # plot variable in object reopened
# 
# ggplot() +
#   geom_stars(data = dcant_3d_read_ncdf %>% 
#                filter(period == "1994 - 2004",
#                       depth == 50)) +
#   facet_grid(MLR_basins~Version_ID_group) +
#   scale_fill_viridis_b(breaks = c(-Inf, seq(0,16,2), Inf),
#                        na.value = "transparent")
# 
# ggplot() +
#   geom_stars(data = dcant_3d_read_mdim %>% 
#                filter(period == "1994 - 2004",
#                       depth == 50)) +
#   facet_grid(MLR_basins~Version_ID_group) +
#   scale_fill_viridis_b(breaks = c(-Inf, seq(0,16,2), Inf),
#                        na.value = "transparent")




```



