---
title: "OIA computation"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

# Libraries

```{r load_libraries_specific, include = FALSE}

library(stars)
library(seacarb)
library(tidync)
library(lubridate)

```

# Basinmask

```{r select_basinmask_5}

basinmask <- basinmask %>% 
  filter(MLR_basins == "5") %>% 
  select(lon, lat, basin_AIP)

```

# Path to files

```{r define_paths_to_access_eMLR_files, include = FALSE}

# path to eMLR estimates of delta Cant

path_observations <-
  paste0(path_root, "/observations/")

path_preprocessing    <-
  paste0(path_observations, "preprocessing/")

path_out <-   paste0(path_observations, "output_publication_compressed/")


# path to ocean interior temperature reconstructions

path_temperature <- 
  "/nfs/kryo/work/updata/cheng/CZ16_v3_IAP_Temperature_gridded_1month_netcdf/Monthly"

# path to ocean interior DIC reconstructions

path_mobo <- 
  "/nfs/kryo/work/updata/mobo-dic/"

# path to OIA data generated for this study

path_OIA <-   "/nfs/kryo/work/jenmueller/ocean_interior_acidification/"


```

# Read data

## Delta Cant

```{r test_interior_dcant_files, eval=FALSE}
library(units)
install_unit(symbol = "decade", def = "10 years")

file_out <- paste0(path_out, "dcant_emlr_cstar_mueller_94-04-14.nc")

dcant_3d_read_mdim <-
  read_mdim(file_out)

# st_get_dimension_values(dcant_3d_read_mdim, "depth")

ggplot() +
  geom_stars(data = dcant_3d_read_mdim %>% 
               filter(period == "1994 - 2004",
                      depth == set_units(50, m))) +
  facet_grid(MLR_configuration ~ MLR_basin_mask) +
  scale_fill_viridis_b(breaks = c(-Inf, seq(0,16,2), Inf),
                       na.value = "transparent")


dcant_3d_tibble <- dcant_3d_read_mdim %>% 
               filter(MLR_configuration == "Standard case",
                      MLR_basin_mask == "3",
                      period == "1994 - 2004") %>%
  as_tibble()

rm(dcant_3d_read_mdim, file_out)

dcant_3d_tibble <- dcant_3d_tibble %>% 
  drop_na()

# remove negative delta Cant
# dcant_3d_tibble <- dcant_3d_tibble
#   mutate(dcant = if_else(dcant < 0, 0, dcant))

dcant_3d_tibble %>%
  filter(depth == set_units(500,m),
         MLR_configuration == "Standard case",
         MLR_basin_mask == "3") %>%
  drop_units() %>% 
  ggplot() +
  geom_raster(aes(lon, lat, fill = dcant)) +
  facet_grid(MLR_basin_mask ~ MLR_configuration) +
  scale_fill_viridis_b(breaks = c(-Inf, seq(0, 16, 2), Inf),
                       na.value = "transparent")


file_out <- paste0(path_out, "volume_mask_emlr_cstar_mueller_94-04-14.nc")

dcant_3d_read_mdim <-
  read_mdim(file_out)

dcant_3d_read_mdim %>% 
  st_get_dimension_values("depth")

volume <- dcant_3d_read_mdim %>%
  as_tibble() %>% 
  drop_na()

file_out <- paste0(path_out, "inv_dcant_emlr_cstar_mueller_94-04-14.nc")

dcant_3d_read_mdim <-
  read_mdim(file_out)

dcant_3d_read_mdim %>% st_get_dimension_values("lat")

dcant_inv <- dcant_3d_read_mdim %>% 
               filter(MLR_configuration == "Standard case",
                      MLR_basin_mask == "3",
                      period == "1994 - 2004") %>%
  as_tibble() %>% 
  drop_na()

file_out <- paste0(path_out, "surface_area_mask_emlr_cstar_mueller_94-04-14.nc")

dcant_3d_read_mdim <-
  read_mdim(file_out)

surface_area <- dcant_3d_read_mdim %>% 
  as_tibble() %>% 
  drop_na()


volume <- full_join(volume,
                    surface_area)

p1 <-
  left_join(dcant_3d_tibble,
            volume) %>%
  filter(depth <= set_units(3000, m)) %>%
  drop_units() %>%
  group_by(lat, lon) %>%
  summarise(dcant = sum(dcant * 1.03 * volume / 1000) / mean(surface_area)) %>%
  ungroup() %>%
  ggplot(aes(lon, lat, fill = dcant)) +
  geom_tile() +
  scale_fill_divergent(limits = c(-2, 2) * 1e1) +
  labs(title = "3000") +
  coord_quickmap()

p2 <-
  left_join(dcant_3d_tibble,
            volume) %>%
  filter(depth <= set_units(2500, m)) %>%
  drop_units() %>%
  group_by(lat, lon) %>%
  summarise(dcant = sum(dcant * 1.03 * volume / 1000) / mean(surface_area)) %>%
  ungroup() %>%
  ggplot(aes(lon, lat, fill = dcant)) +
  geom_tile() +
  scale_fill_divergent(limits = c(-2, 2) * 1e1) +
  labs(title = "2500") +
  coord_quickmap()

p3 <-
  left_join(dcant_3d_tibble,
            volume) %>%
  filter(depth <= set_units(3000, m)) %>%
  mutate(volume = if_else(depth == set_units(3000, m),
                          volume * 0.5,
                          volume)) %>%
  drop_units() %>%
  group_by(lat, lon) %>%
  summarise(dcant = sum(dcant * 1.03 * volume / 1000) / mean(surface_area)) %>%
  ungroup() %>%
  ggplot(aes(lon, lat, fill = dcant)) +
  geom_tile() +
  scale_fill_divergent(limits = c(-2, 2) * 1e1) +
  labs(title = "3000 halfed") +
  coord_quickmap()

p4 <-
  dcant_inv %>%
  drop_units() %>%
  ggplot(aes(lon, lat, fill = dcant_inv)) +
  geom_tile() +
  scale_fill_divergent(limits = c(-2, 2) * 1e1,
                       na.value = "white") +
  labs(title = "3000 direct") +
  coord_quickmap()


p1 + p2 + p3 + p4



```

```{r read_interior_dcant_files}
library(units)

file_out <- paste0(path_out, "dcant_emlr_cstar_mueller_94-04-14.nc")

dcant_3d_read_mdim <-
  read_mdim(file_out,
            make_units = FALSE)

ggplot() +
  geom_stars(data = dcant_3d_read_mdim %>% 
               filter(period == "1994 - 2004",
                      depth == set_units(50, m))) +
  facet_grid(MLR_basin_mask~MLR_configuration) +
  scale_fill_viridis_b(breaks = c(-Inf, seq(0,16,2), Inf),
                       na.value = "transparent")


dcant_3d_tibble <- dcant_3d_read_mdim %>% 
               # filter(MLR_configuration == "Standard case",
               #        MLR_basin_mask == "3") %>% 
  as_tibble() %>% 
  drop_units()

rm(dcant_3d_read_mdim, file_out)

dcant_3d_tibble <- dcant_3d_tibble %>% 
  drop_na()

# remove negative delta Cant
# dcant_3d_tibble <- dcant_3d_tibble
#   mutate(dcant = if_else(dcant < 0, 0, dcant))

dcant_3d_tibble %>%
  filter(depth == 500,
         MLR_configuration == "Standard case",
         MLR_basin_mask == "3") %>%
  ggplot() +
  geom_raster(aes(lon, lat, fill = dcant)) +
  facet_grid(MLR_basin_mask ~ MLR_configuration) +
  scale_fill_viridis_b(breaks = c(-Inf, seq(0, 16, 2), Inf),
                       na.value = "transparent")

```

## Total Cant 1994

```{r tcant_sabine_2004}

S04_cant_3d <-
  read_csv(paste(path_preprocessing,
                 "S04_tcant_3d.csv",
                 sep = ""))

# remove negative delta Cant
# S04_cant_3d <- S04_cant_3d %>%
#   mutate(tcant = if_else(tcant < 0, 0, tcant))

```


## GLODAP climatologies

```{r read_GLODAP_climatology_errors}

path_glodapv2_2016b   <-
  "/nfs/kryo/work/datasets/gridded/ocean/interior/observation/glodap/v2.2016b/"

file_list <- c(
  "GLODAPv2.2016b.TAlk.nc",
  "GLODAPv2.2016b.TCO2.nc"
)


for (file in file_list) {
  # file <- file_list[1]
  
  print(file)
  # open file

  # extract parameter name
  
  parameter <-
    str_split(file, pattern = "GLODAPv2.2016b.", simplify = TRUE)[2]
  parameter <-
    str_split(parameter, pattern = ".nc", simplify = TRUE)[1]
  parameter <- paste0(parameter,"_error")
  
    
  clim <-
    read_stars(paste(path_glodapv2_2016b, file, sep = ""),
              sub = parameter)
  
  #convert to table
  
  clim_tibble <- clim %>%
    as_tibble()
  
  # harmonize column names
  
  clim_tibble <- clim_tibble %>%
    rename(lat = y,
           lon = x,
           depth = depth_surface)
  
  clim_tibble <- clim_tibble %>%
    mutate(lat = lat - 90,
           lon = lon + 20)

  # clim_tibble %>% 
  #   filter(depth == 0) %>% 
  #   ggplot(aes(lon, lat, fill = NO3)) +
  #   geom_raster()
  
  # join with basin mask and remove data outside basin mask
  
  clim_tibble <- inner_join(clim_tibble, basinmask)

  # determine bottom depth
  
  bottom_depth <- clim_tibble %>%
    filter(!is.na(!!sym(parameter))) %>%
    group_by(lon, lat) %>%
    summarise(bottom_depth = max(depth)) %>%
    ungroup()
  
  # remove data below bottom depth
  clim_tibble <- left_join(clim_tibble, bottom_depth)
  rm(bottom_depth)
  
  clim_tibble <- clim_tibble %>%
    filter(depth <= bottom_depth) %>%
    select(-bottom_depth)
  
  # fill NAs with closest value along longitude
  
  clim_tibble <- clim_tibble %>%
    group_by(lat, depth, basin_AIP) %>%
    arrange(lon) %>%
    fill(!!sym(parameter), .direction = "downup") %>%
    ungroup()
  
  # remove NAs
  
  clim_tibble <- clim_tibble %>%
    drop_na()
  
  # plot maps
  
  print(p_map_climatology(df = clim_tibble,
                          var = parameter))
  

  # write csv file
  
  if (exists("GLODAP_predictors_error")) {
    GLODAP_predictors_error <- full_join(GLODAP_predictors_error, clim_tibble)
  }
  
  if (!exists("GLODAP_predictors_error")) {
    GLODAP_predictors_error <- clim_tibble
  }
  
}

rm(clim, clim_tibble, parameter, file, file_list)


```



```{r load_GLODAPv2_2016b_MappedClimatologies_interior_mapping}

variables <-
  c("TCO2", "TAlk", "PO4", "silicate", "NO3")

# i_variable <- variables[1]

for (i_variable in variables) {
  temp <- read_csv(paste(
    path_preprocessing,
    paste("GLODAPv2_2016_MappedClimatology_", i_variable, ".csv", sep = ""),
    sep = ""
  ))
  
  if (exists("GLODAP_predictors")) {
    GLODAP_predictors <- full_join(GLODAP_predictors, temp)
  }
  
  if (!exists("GLODAP_predictors")) {
    GLODAP_predictors <- temp
  }
}

rm(temp, i_variable, variables)

GLODAP_predictors <- GLODAP_predictors %>%
  rename(phosphate = PO4,
         nitrate = NO3,
         talk = TAlk,
         tco2 = TCO2)

# removed na's attributable to slightly different coverage of predictor fields
GLODAP_predictors <- GLODAP_predictors %>%
  drop_na()

```



## World Ocean Atlas 2018  

```{r load_WOA18}

WOA18_predictors <-
  read_csv(paste(path_preprocessing,
                 "WOA18_sal_temp.csv",
                 sep = ""))

WOA18_predictors_nuts_O2 <-
  read_csv(paste(path_preprocessing,
                 "WOA18_nuts_O2.csv",
                 sep = ""))

```


## Cheng temperature

```{r read_cheng_temperature, eval=FALSE}

# loop over reference years, plus/minus enveloppe years, and month
# to obtain a decadal averaged temperature field


for (i_tref in c(1994, 2004, 2014)) {
  # i_tref <- 1994
  print(i_tref)
  
  for (i_year in i_tref + seq(-3, 3, 1)) {
    # i_year <- i_tref + seq(-2,2,1)[1]
    print(i_year)
    
    for (i_month in c("01",
                      "02",
                      "03",
                      "04",
                      "05",
                      "06",
                      "07",
                      "08",
                      "09",
                      "10",
                      "11",
                      "12")) {
      # i_month <- "01"
      print(i_month)
      
      i_temperature_file <-
        paste0("CZ16_1_2000m_Temp_year_",
               i_year,
               "_month_",
               i_month,
               ".nc")
      print(i_temperature_file)
      
      tidy_df <-
        tidync(paste(path_temperature, i_temperature_file, sep = "/"))
      
      tibble_df <- tidy_df %>%
        hyper_tibble()
      
      tibble_df <-
        tibble_df %>%
        mutate(temp = if_else(temp == 999, NaN, temp))
      
      if (exists("temperature_year")) {
        temperature_year <- bind_rows(temperature_year, tibble_df)
      }
      
      if (!exists("temperature_year")) {
        temperature_year <- tibble_df
      }
      
    }
    
    temperature_year <- temperature_year %>%
      group_by(lat, lon, depth_std) %>%
      summarise(temp = mean(temp, na_rm = TRUE)) %>%
      ungroup()
    
    temperature_year <- temperature_year %>%
      mutate(year = i_year)
    
    if (exists("temperature_decade")) {
      temperature_decade <-
        bind_rows(temperature_decade, temperature_year)
    }
    
    if (!exists("temperature_decade")) {
      temperature_decade <- temperature_year
    }
    
    rm(temperature_year)
    
    gc()
    
  }
  
  
  temperature_decade <- temperature_decade %>%
    group_by(lat, lon, depth_std) %>%
    summarise(temp = mean(temp, na_rm = TRUE)) %>%
    ungroup()
  
  temperature_decade <- temperature_decade %>%
    mutate(tref = i_tref)
  
  if (exists("temperature_all")) {
    temperature_all <-
      bind_rows(temperature_all, temperature_decade)
  }
  
  if (!exists("temperature_all")) {
    temperature_all <- temperature_decade
  }
  
  rm(temperature_decade)
  
  gc()
  
}

rm(tibble_df,tidy_df, i_month, i_temperature_file, i_tref, i_year)

# rm(temperature_all)

temperature_all <-
  temperature_all %>%
  rename(depth = depth_std)

temperature_all %>%
  distinct(depth) %>% 
  pull

# change surface depth level from 1 to 0 for consistency with other data
temperature_all <-
  temperature_all %>%
  mutate(depth = if_else(depth == 1, 0, depth))

temperature_all %>%
  filter(depth == 500) %>%
  ggplot(aes(lon, lat, fill = temp)) +
  geom_tile() +
  scale_fill_viridis_c() +
  facet_wrap(~tref) +
  coord_quickmap()

# calculate decadal temperature change
temperature_all <- temperature_all %>%
  arrange(tref) %>%
  group_by(lon, lat, depth) %>%
  mutate(delta_temp = temp - first(temp)) %>%
  ungroup() %>% 
  select(lon, lat, depth, tref, delta_temp)


temperature_all %>%
  filter(depth == 500) %>%
  ggplot(aes(lon, lat, fill = delta_temp)) +
  geom_tile() +
  scale_fill_gradient2() +
  facet_wrap( ~ tref) +
  coord_quickmap()


```


## MOBO-DIC

```{r read_mobo-dic, eval=FALSE}

mobo_dic_dates <-
  read_ncdf(paste0(path_mobo, "MPI_MOBO-DIC_2004-2019_Oct2022.nc")) %>%
  st_get_dimension_values("juld")


mobo_dic_dates <-
mobo_dic_dates %>% 
  as_tibble() %>% 
  rename(date = value) %>% 
  mutate(year = year(date),
         juld = row_number()) %>% 
  select(juld, year)



mobo_dic <-
  tidync(paste0(path_mobo, "MPI_MOBO-DIC_2004-2019_Oct2022.nc")) %>%
  hyper_tibble()

mobo_dic <-
  full_join(mobo_dic, mobo_dic_dates)

rm(mobo_dic_dates)

mobo_dic_clim <-
  mobo_dic %>%
  filter(year %in% c(seq(2004,2006,1), seq(2014,2016,1))) %>%
  mutate(tref = if_else(year < 2010, "2004", "2014")) %>% 
  group_by(tref, lon, lat, depth) %>%
  summarise(DIC = mean(DIC, na.rm = TRUE)) %>%
  ungroup()

rm(mobo_dic)

mobo_dic_clim %>% 
  distinct(lat) %>% 
  pull

mobo_dic_clim %>% 
  distinct(lon) %>% 
  pull

mobo_dic_clim <-
  mobo_dic_clim %>%
  mutate(lon = if_else(lon < 20, lon + 360, lon))

mobo_dic_clim %>% 
  distinct(depth) %>% 
  pull

mobo_dic_clim %>% 
  filter(depth == 10) %>% 
  ggplot(aes(lon, lat, fill = DIC)) +
  geom_raster() +
  coord_quickmap() +
  scale_fill_viridis_c() +
  facet_wrap(~ tref)

mobo_dic_clim %>% 
  filter(depth == 10) %>%
  arrange(tref) %>% 
  group_by(lat, lon) %>%
  mutate(delta_DIC = DIC - lag(DIC)) %>% 
  ungroup() %>% 
  ggplot(aes(lon, lat, fill = delta_DIC)) +
  geom_raster() +
  coord_quickmap() +
  scale_fill_divergent() +
  facet_wrap(~ tref)

gc()

```


# Join data

## WOA18 + GLODAP

WOA18 and GLODAP predictor climatologies are merged. Only horizontal grid cells with observations from both predictor fields are kept.

```{r join_WOA18_GLODAP_predictors}

# join deep water predictors

predictors <- right_join(GLODAP_predictors,
                          WOA18_predictors)

predictors <- rquery::natural_join(predictors, WOA18_predictors_nuts_O2,
                           by = c("lon", "lat", "depth", "basin_AIP"),
                           jointype = "LEFT") %>% 
  as_tibble()

predictors <- predictors %>% 
  drop_na()


rm(GLODAP_predictors, WOA18_predictors_nuts_O2, WOA18_predictors)

```

## Predictors + Cant

```{r join_predictors_dcant}

# predictors %>% distinct(depth) %>% pull()
# S04_cant_3d %>% distinct(depth) %>% pull()
# dcant_3d_tibble %>% distinct(depth) %>% pull()

# create depth grid for which all reconstructions are available

coord_grid <- predictors %>% 
  distinct(lon, lat, depth)

coord_grid <-
  inner_join(coord_grid,
             dcant_3d_tibble %>%
               distinct(lon, lat, depth))

coord_grid <-
  inner_join(coord_grid,
             S04_cant_3d %>%
               distinct(lon, lat, depth))

coord_grid <-
  inner_join(coord_grid,
             GLODAP_predictors_error %>%
               distinct(lon, lat, depth))



# restrict CO2 fields to common grid

predictors <- inner_join(
  predictors,
  coord_grid
)

dcant_3d_tibble <- inner_join(
  dcant_3d_tibble,
  coord_grid
)

S04_cant_3d <- inner_join(
  S04_cant_3d,
  coord_grid
)

GLODAP_predictors_error <- inner_join(
  GLODAP_predictors_error,
  coord_grid
)

rm(coord_grid)

# join data frames

DIC_1994 <- 
  inner_join(predictors,
             dcant_3d_tibble %>% filter(period == "1994 - 2004") %>% 
               select(-period))

DIC_1994 <- DIC_1994 %>% 
  mutate(tco2 = tco2 - 0.8 * dcant)
  

DIC_2004 <- DIC_1994 %>% 
  mutate(tco2 = tco2 + dcant)

DIC_1994 <- DIC_1994 %>% 
  select(-dcant)

DIC_2004 <- DIC_2004 %>% 
  select(-dcant)


DIC_2014 <-
  inner_join(DIC_2004,
             dcant_3d_tibble %>% filter(period == "2004 - 2014") %>%
               select(-period))

DIC_2014 <- DIC_2014 %>% 
  mutate(tco2 = tco2 + dcant) %>% 
  select(-dcant)


DIC_1800 <- inner_join(
  DIC_1994 %>%   filter(MLR_configuration == "Standard case",
                        MLR_basin_mask == "3"),
  S04_cant_3d %>% select(lon, lat, depth, tcant)
)

DIC_1800 <- DIC_1800 %>% 
  mutate(tco2 = tco2 - tcant) %>% 
  select(-tcant)


DIC <- bind_rows(
  DIC_1800 %>% mutate(tref = "1800"),
  DIC_1994 %>% mutate(tref = "1994"),
  DIC_2004 %>% mutate(tref = "2004"),
  DIC_2014 %>% mutate(tref = "2014")
)

rm(DIC_1800, DIC_1994, DIC_2004, DIC_2014, predictors, dcant_3d_tibble, S04_cant_3d)

```

```{r include_TCO2_TAlk_uncertainty}

DIC_clim_uncertainty <- inner_join(
  DIC %>% filter(MLR_configuration == "Standard case",
                 MLR_basin_mask == "3"),
  GLODAP_predictors_error %>% select(-basin_AIP)
)


DIC <- bind_rows(
  DIC_clim_uncertainty %>%
    mutate(
      MLR_configuration = "high DIC low TA",
      tco2 = tco2 + TCO2_error,
      talk = talk - TAlk_error
    ),
  DIC_clim_uncertainty %>%
    mutate(
      MLR_configuration = "low DIC high TA",
      tco2 = tco2 - TCO2_error,
      talk = talk + TAlk_error
    ),
  DIC_clim_uncertainty %>%
    mutate(
      MLR_configuration = "high DIC",
      tco2 = tco2 + TCO2_error
    ),
  DIC_clim_uncertainty %>%
    mutate(
      MLR_configuration = "low DIC",
      tco2 = tco2 - TCO2_error
    ),
  DIC
)

DIC <- DIC %>% 
  select(-c(TAlk_error, TCO2_error))

rm(DIC_clim_uncertainty, GLODAP_predictors_error)

```



```{r join_dCant_temperature, eval=FALSE}

# create DIC fields with variable temperature

DIC_temp <- DIC %>%
  filter(tref != 1800,
         MLR_configuration == "Standard case",
         MLR_basin_mask == 3) %>%
  mutate(MLR_configuration = "dCant + temp")

DIC_temp %>%
  distinct(tref, MLR_configuration, MLR_basin_mask)

DIC_depths <- DIC_temp %>% 
  distinct(depth) %>% 
  filter(depth <= 2000) %>% 
  pull()

# extend temperature field with DIC depth for interpolation
depth_grid <-
  expand_grid(
    temperature_all %>%
      distinct(lat, lon, tref),
    depth = DIC_depths
  )

temperature_all <-
  full_join(temperature_all,
            depth_grid)

rm(depth_grid)

temperature_all <-
  temperature_all %>%
  group_by(lon, lat, tref) %>%
  mutate(count_available = sum(!is.na(delta_temp))) %>% 
  ungroup()


temperature_all_surface <-
  temperature_all %>%
  filter(count_available == 1) %>%
  select(-count_available) %>%
  filter(!is.na(delta_temp))

temperature_all_int <-
  temperature_all %>%
  filter(count_available >= 2) %>% 
  select(-count_available) %>% 
  group_by(lon, lat, tref) %>%
  mutate(delta_temp = approxfun(depth, delta_temp, rule = 1)(depth)) %>%
  ungroup() %>% 
  filter(!is.na(delta_temp))

temperature_all <- bind_rows(
  temperature_all_surface,
  temperature_all_int
)

rm(
  temperature_all_surface,
  temperature_all_int
)

temperature_all <-
  temperature_all %>%
  filter(depth %in% DIC_depths)

temperature_all <- temperature_all %>% 
  mutate(tref = as.character(tref))

temperature_all <- temperature_all %>% 
  mutate(lon = lon - 0.5,
         lon = if_else(lon < 20, lon + 360, lon))

DIC_temp <- inner_join(
  DIC_temp,
  temperature_all)

DIC_temp <-
  DIC_temp %>%
  mutate(temp = temp + delta_temp) %>%
  select(-delta_temp)

DIC <- bind_rows(
  DIC,
  DIC_temp
)

rm(DIC_temp, temperature_all)

```



```{r join_dCant_DIC, eval=FALSE}

# create DIC fields with variable temperature

DIC_DIC <- DIC %>%
  filter(tref %in% c("2004", "2014"),
         MLR_configuration %in% c("Standard case", "dCant + temp"),
         MLR_basin_mask == 3) %>%
  mutate(MLR_configuration = if_else(
    MLR_configuration == "Standard case",
    "DIC",
    "DIC + temp"
  ))

mobo_dic_clim <- 
  mobo_dic_clim %>% 
  mutate(depth = if_else(depth == 2.5, 0, depth))

mobo_dic_clim %>% 
  distinct(depth) %>% 
  pull


DIC_DIC <- inner_join(
  DIC_DIC,
  mobo_dic_clim)

DIC_DIC <-
  DIC_DIC %>%
  mutate(tco2 = DIC) %>%
  select(-DIC)

DIC <- bind_rows(
  DIC,
  DIC_DIC
)

rm(DIC_DIC, mobo_dic_clim)

gc()

```

# Set-up computation

```{r set_up}

# table with cases to loop over
cases <- DIC %>%
  distinct(MLR_configuration, MLR_basin_mask)

# cases <- cases %>% 
#   filter(MLR_basin_mask == "none")

# cases <- cases %>% 
#   filter(MLR_basin_mask == "3") %>% 
#   slice(-c(2:6))



# definition of functions to compute incremental and total differences

calc_delta_total <- function(x)
  (x - first(x))

calc_delta_interval <- function(x)
  (x - lag(x, default = first(x)))

```



# Compute acidification trends

```{r compute_acidification_trends, eval=FALSE}

for (i in 1:nrow(cases)) {
  # i <- 1
  
  i_MLR_configuration <-  cases[i, ]$MLR_configuration
  i_MLR_basin_mask <-  cases[i, ]$MLR_basin_mask
  
  i_DIC <- DIC %>%
    filter(MLR_configuration == i_MLR_configuration,
           MLR_basin_mask == i_MLR_basin_mask)
  
  
  acidification <- i_DIC %>%
    # head(6) %>%
    mutate(
      sir(
        flag = 15,
        var1 = talk * 1e-6,
        var2 = tco2 * 1e-6,
        S = sal,
        T = temp,
        P = depth / 10,
        Pt = phosphate * 1e-6,
        Sit = silicate * 1e-6,
        k1k2 = "s20",
        kf = "dg",
        pHscale = "T"
      )
    )
  
  rm(i_DIC)
  gc()
  
  acidification <- acidification %>%
    select(
      lon, lat, depth, tref,
      MLR_basin_mask, MLR_configuration,
      tco2, pH, CO3, OmegaAragonite, OmegaCalcite, SIR, H_free
    )
  
  acidification <- acidification %>%
    mutate(
      CO3 = CO3 * 1e6,
      H_free = H_free * 1e3
    )
  
  acidification <- acidification %>%
    arrange(tref) %>%
    group_by(lat, lon, depth, MLR_configuration, MLR_basin_mask) %>%
    mutate(across(
      .cols = c(
        tco2,
        pH,
        CO3,
        OmegaAragonite,
        OmegaCalcite,
        SIR,
        H_free
      ),
      .fns = list(delta_total = calc_delta_total, delta_interval = calc_delta_interval)
    )) %>%
    ungroup()

  acidification %>%
    write_csv(paste0(path_OIA,"OIA_",i_MLR_configuration,"_",i_MLR_basin_mask,".csv"))
  
  rm(acidification)
  gc()
  
}

```

# Compute buffer factors

## direct approach

```{r compute_buffer_factors_direct, eval=FALSE}

for (i in 1:nrow(cases)) {
  # i <- 1
  
  i_MLR_configuration <-  cases[i,]$MLR_configuration
  i_MLR_basin_mask <-  cases[i,]$MLR_basin_mask
  
  
  i_DIC <- DIC %>%
    filter(MLR_configuration == i_MLR_configuration,
           MLR_basin_mask == i_MLR_basin_mask)
  
  buffer <- i_DIC %>%
    # filter(lon == 190.5,
    #        lat == 0.5,
    #        depth == 0) %>%
    mutate(
      buffesm(
        flag = 15,
        var1 = talk * 1e-6,
        var2 = tco2 * 1e-6,
        S = sal,
        T = temp,
        P = depth / 10,
        Pt = phosphate * 1e-6,
        Sit = silicate * 1e-6,
        k1k2 = "s20",
        kf = "dg",
        pHscale = "T"
      )
    )
  
  rm(i_DIC)
  gc()
  
  buffer <- buffer %>%
    select(
      c(
        lon,
        lat,
        depth,
        tref,
        MLR_basin_mask,
        MLR_configuration,
        gammaDIC,
        betaDIC,
        omegaDIC,
        R
      )
    )
  
  buffer_trend <- buffer %>%
    arrange(tref) %>%
    group_by(lat, lon, depth, MLR_configuration, MLR_basin_mask) %>%
    mutate(across(
      .cols = c(gammaDIC,
                betaDIC,
                omegaDIC,
                R),
      .fns = list(delta_total = calc_delta_total, delta_interval = calc_delta_interval)
    )) %>%
    ungroup()
  
  rm(buffer)
  gc()
  
  buffer_trend %>%
    write_csv(paste0(path_OIA,"buffer_",i_MLR_configuration,"_",i_MLR_basin_mask,".csv"))
  
  rm(buffer_trend)
  gc()
  
}


```

## incremental DIC increase

```{r compute_buffer_factors_DIC_increase}

# cases <- cases %>% 
#   filter(MLR_configuration == "Standard case",
#          MLR_basin_mask == "3")

for (i in 1:nrow(cases)) {
  # i <- 1
  
  i_MLR_configuration <-  cases[i, ]$MLR_configuration
  i_MLR_basin_mask <-  cases[i, ]$MLR_basin_mask
  
  i_DIC <- DIC %>%
    filter(MLR_configuration == i_MLR_configuration,
           MLR_basin_mask == i_MLR_basin_mask)
  
  i_DIC <- i_DIC %>% 
    mutate(tco2 = tco2 + 5)
  
  acidification <- i_DIC %>%
    # head(6) %>%
    mutate(
      sir(
        flag = 15,
        var1 = talk * 1e-6,
        var2 = tco2 * 1e-6,
        S = sal,
        T = temp,
        P = depth / 10,
        Pt = phosphate * 1e-6,
        Sit = silicate * 1e-6,
        k1k2 = "s20",
        kf = "dg",
        pHscale = "T"
      )
    )
  
  rm(i_DIC)
  gc()
  
  acidification <- acidification %>%
    select(
      lon, lat, depth, tref,
      MLR_basin_mask, MLR_configuration,
      tco2, pH, CO3, OmegaAragonite, OmegaCalcite, SIR, H_free
    )
  
  acidification <- acidification %>%
    mutate(
      CO3 = CO3 * 1e6,
      H_free = H_free * 1e3
    )
  
  acidification <- acidification %>%
    arrange(tref) %>%
    group_by(lat, lon, depth, MLR_configuration, MLR_basin_mask) %>%
    mutate(across(
      .cols = c(
        tco2,
        pH,
        CO3,
        OmegaAragonite,
        OmegaCalcite,
        SIR,
        H_free
      ),
      .fns = list(delta_total = calc_delta_total, delta_interval = calc_delta_interval)
    )) %>%
    ungroup()
  
  acidification %>%
    write_csv(paste0(path_OIA,"OIA_",i_MLR_configuration,"_",i_MLR_basin_mask,"_DIC_addition.csv"))
  
  rm(acidification)
  gc()
  
}

```


```{r write_output_files_stars, eval=FALSE}



# convert from tibble to stars object
acidification_trend_stars <- st_as_stars(
  acidification_trend,
  dims = c(
    "lon",
    "lat",
    "depth",
    "tref",
    "MLR_basin_mask",
    "MLR_configuration"
  )
)

# assign coordinate system to horizontal (lon, lat) coordinates
# st_crs(dcant_inv_out_stars) <- "+proj=longlat"
st_crs(acidification_trend_stars) <- st_crs(4326)

# plot variable per depth level
# ggplot() +
#   geom_stars(data = acidification_trend_stars %>% 
#                filter(period == "1994 - 2004",
#                       depth == 50)) +
#   facet_grid(MLR_basin_mask~MLR_configuration) +
#   scale_fill_viridis_b(breaks = c(-Inf, seq(0,16,2), Inf),
#                        na.value = "transparent")


file_out <- paste0(path_OIA, "OIA_pH.nc")

# write stars object to .nc file

names_OIA <-
  acidification_trend_stars %>%
  names()

acidification_trend_stars %>% 
  select(names_OIA[12]) %>% 
  write_mdim(file_out)

# # reopen .nc file with all available stars functions
# dcant_3d_read_ncdf <-
#   read_ncdf(file_out)
# dcant_3d_read_mdim <-
#   read_mdim(file_out)
# 
# # plot variable in object reopened
# 
# ggplot() +
#   geom_stars(data = dcant_3d_read_ncdf %>% 
#                filter(period == "1994 - 2004",
#                       depth == 50)) +
#   facet_grid(MLR_basin_mask~MLR_configuration) +
#   scale_fill_viridis_b(breaks = c(-Inf, seq(0,16,2), Inf),
#                        na.value = "transparent")
# 
# ggplot() +
#   geom_stars(data = dcant_3d_read_mdim %>% 
#                filter(period == "1994 - 2004",
#                       depth == 50)) +
#   facet_grid(MLR_basin_mask~MLR_configuration) +
#   scale_fill_viridis_b(breaks = c(-Inf, seq(0,16,2), Inf),
#                        na.value = "transparent")




```



